\documentclass[12pt]{article}
\usepackage{hyperref}
\usepackage[singlespacing]{setspace}
\usepackage[margin=1in]{geometry}
\usepackage{indentfirst}   % Indents first paragraph. change if u want ig
\usepackage{setspace} 
\usepackage{qtree}
\usepackage[most]{tcolorbox}
\usepackage{titling}
\usepackage{float}

\hypersetup{
    bookmarks=false,                                % show bookmarks bar?
    pdftitle={Software Requirement Specification},  % title
    pdfauthor={Jean-Philippe Eisenbarth},           % author
    pdfsubject={TeX and LaTeX},                     % subject of the document
    pdfkeywords={TeX, LaTeX, graphics, images},     % list of keywords
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=blue,         % color of internal links
    citecolor=black,        % color of links to bibliography
    filecolor=black,        % color of file links
    urlcolor=purple,        % color of external links
    linktoc=page            % only page is linked
}%
\def\myversion{1.0 }
\date{}
%\title{%

%}
\begin{document}

\begin{flushleft}
    \rule{16cm}{5pt}\vskip1cm
    \begin{bfseries}
        \Huge{Milestone 6 Evaluation}\\
        \vspace{1.9cm}
        VehID\\
        \vspace{1.2cm}
        \LARGE{Version \myversion}\\
        \vspace{1.2cm}
        \textnormal{Remington Greko, Spencer Hirsch, Thomas Johnson, Alexis Nagle} \\
        \vspace{1.2cm}
        \textnormal{Project Advisor: Dr. Marius Silaghi}\\
        \textnormal{Project Client: Clayton Levins, Executive Director of Smart North Florida} \\
        \vspace{1.2cm}
        \textnormal{\today}\\
    \end{bfseries}
\end{flushleft}

\pagebreak

\tableofcontents

\pagebreak

\section{Progress Matrix}

\noindent\begin{center}
  \begin{tabular}{||p{3cm}|p{2.6cm}|p{2.3cm}|p{1.6cm}|p{1.6cm}|p{1.2cm}|p{2cm}||}
    \hline
    \hline
    \textbf{Task} & \textbf{Completion \%} & \textbf{Remington} & \textbf{Spencer} & \textbf{Thomas} & \textbf{Alexis} & \textbf{To-do} \\
    \hline
    Test/Demo System & 100\% & 50\% & 0\% & 50\% & 0\%  & NA\\
    \hline
    Conduct Evaluation and Analyze Results & 100\% & 0\% & 50\% & 0\% & 50\%  & NA\\
    \hline
    Create User/Developer Manual & 100\% & 25\% & 25\% & 25\% & 25\%  & NA\\
    \hline
    Create Demo Video & 100\% & 0\% & 50\% & 0\% & 50\%  & NA\\
    \hline
    Sprint Planning & 100\% & 25\% & 25\% & 25\% & 25\%  & NA\\
    \hline
    Milestone Evaluation & 100\% & 25\% & 25\% & 25\% & 25\%  & NA\\
    \hline
    \hline
  \end{tabular}
\end{center}

\section{Discussion - Milestone 6}

\subsection{Tasks}

\noindent\textbf{Test/Demo System:} For this milestone, we have completed our project and it was now time to 
perform tests to ensure that our appplication is working. This involved testing that each component was working with
one another. We have been continuously testing our neural networks as they are built off of one another. However, this
time we finally linked our neural network subsystem with our web application and database.

\medskip

\noindent\textbf{Conduct Evaluation and Analyze Results:} Now that we have completed our project we needed to reflect
on the performance of our system. This included manually validating our test data from a neural network subsystem as
well as ensuring the usability of our web application and database.

\medskip

\noindent\textbf{Create User/Developer Manual:} We created our User and Developer Manual is this milestone touching
on the technical components of our project. For the user manual we discuss how one may use our system. Our developer manual
primarily focuses on the way our system is set up and how each individual component works.

\medskip

\noindent\textbf{Create Demo Video:}  We recorded a demonstration as outlined
on Dr. Chan's website for the showcase.


\medskip

\noindent\textbf{Sprint Planning:} As with our previous milestones, at the beginning of each milestone we discuss the work that needs to be accomplished
over the milestone and divide up tasks to ensure efficiency.

\medskip

\noindent\textbf{Milestone Evaluation:} We completed our milestone evaluation to summarize all of our work that we accomplished over the past few weeks,
outlining the tasks that we accomplished. This time allows us to reflect on our work and find any issues that occured allowing us to correct it in the coming
milestone.

\medskip

\subsection{Member Contribution}

\noindent\textbf{Remington Greko:} For this milestone I contributed to creating the web application. I implemented the code to connect the JSON output from the CNNs to the 
database used in the web application. I also made some modifications and fixes to multiple APIs and front-end components as new goals and issues arose throughout
the milestone. Recorded the demo video for the web application. I also worked on completing the milestone evaluation and developer manual focusing on the web application 
and database sections.

\medskip

\noindent\textbf{Spencer Hirsch:} For the milestone I participated in many of our tasks. This included, sprint planning and 
evalulating the performance of the neural network subsystem as well as the web application and database. I also worked on
our Milestone Evaluation Document and the User and Developer Manual.

\medskip

\noindent\textbf{Thomas Johnson:} For this milestone I continued in creating the web application. I continued to expand off of the front end, and once the CRUD functionalities were 
implemented by Remi I added user functionalities to our tabulated display of the data. I added a `view more` button to display more entries in the list, and filtering functionality
to display full or partial matches. I implemenmted the form functionality located in `index.html` to search the database for matches, and display all applicable matches into a modal 
to be displayed for the user. I also did some minor styling to keep displays uniform between pages.
\medskip

\noindent\textbf{Alexis Nagle:} For this milestone, I contributed to many of our tasks. I helped record the demo video for the 
neural network subsystem demonstration. I also worked on conducting the evaluation and including this into both our poster and 
eBook from last milestone. In addition to finishing up those documents, I worked on adding the neural network information to the 
user/developer manual. Just as previous milestones, I also participated in the sprint planning and creation of the milestone evaluation. 

\section{Client}

\subsection{Meeting Date}
Date: Wednesday, April 10, 2024
\subsection{Client Feedback}


\noindent\textbf{Test/Demo System:} We demonstrated our system to our client who was very pleased with the work that
we were able to complete. This was our final meeting so we were able to show him our project in its entirety.

\medskip

\noindent\textbf{Conduct Evaluation and Analyze Results:} We discussed our Neural Network Subsystem evaluation results with our
client. He seemed pleased with how the models were performing, we discussed our hardships with training and testing
our data. Overall, he was pleased with what we were able to complete. In addition to discussing the results from the 
Neural Network we asked our client for ideas of how to evaluate the web application. He gave us useful feedback of what
he would expect us to do for this portion.

\medskip

\noindent\textbf{Create User/Developer Manual:} We did not discuss our User/Developer Manual with our client. We did
however dicuss some of the topics discussed in the document.

\medskip

\noindent\textbf{Create Demo Video:} We did not demonstrate our recorded demonstration to our client, however we performed
a live demo showing how the software works.


\medskip

\noindent\textbf{Sprint Planning:} Our client did not have any concerns with how to work was divided up. He was
pleased with our results of the project.

\medskip

\noindent\textbf{Milestone Evaluation:} Our client did not have any comments on out milestone
evaulation document.



\section{Faculty Advisor}
\subsection{Meeting Date}

Date: Friday, April 12, 2024

\subsection{Advisor Feedback}


\noindent\textbf{Test/Demo System:} Dr. Silaghi seemed please with our demonstration of the system. After showing him our
web application demo he had some questions about how we designed our web application and database.

\medskip

\noindent\textbf{Conduct Evaluation and Analyze Results:} We discussed our evaluation results on the poster with Dr. Silaghi,
he didn't necessarily have any comments on the actual performace of the model.

\medskip

\noindent\textbf{Create User/Developer Manual:} We did not discuss our User/Developer Manual with Dr. Silaghi. Our primary focus
during the meeting was regarding our poster and ebook.

\medskip

\noindent\textbf{Create Demo Video:} We demonstrated our updated web application to Dr. Silaghi, he seems pleased with our progress.

\medskip

\noindent\textbf{Sprint Planning:} Dr. Silaghi did not have any concerns at this time about how we divided work up for this Milestone.
\medskip

\noindent\textbf{Milestone Evaluation:} Dr. Silaghi did not express any concerns regarding our milestone evaluation.

\bigskip

\begin{center}
\begin{tabular}{@{}p{1.9in}p{3in}p{.3in}p{1in}@{}}
  Faculty Advisor Signature: & \hrulefill & Date: & \hrulefill\\
\end{tabular}
\end{center}

\pagebreak

\subsection{Student Evaluation}

\begin{center}

  \begin{tabular}{||p{4cm}|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c||}
    \hline
    \hline
    Remington Greko & 0 &  1 & 2 & 3 & 4 & 5 & 5.5 & 6 & 6.5 & 7 & 7.5 & 8 & 8.5 & 9 & 9.5 & 10\\
    \hline
    Spencer Hirsch & 0 &  1 & 2 & 3 & 4 & 5 & 5.5 & 6 & 6.5 & 7 & 7.5 & 8 & 8.5 & 9 & 9.5 & 10\\
    \hline
    Thomas Johnson & 0 &  1 & 2 & 3 & 4 & 5 & 5.5 & 6 & 6.5 & 7 & 7.5 & 8 & 8.5 & 9 & 9.5 & 10\\
    \hline
    Alexis Nagle & 0 &  1 & 2 & 3 & 4 & 5 & 5.5 & 6 & 6.5 & 7 & 7.5 & 8 & 8.5 & 9 & 9.5 & 10\\
    \hline
    \hline
    \end{tabular}
\end{center}


\begin{center}
\begin{tabular}{@{}p{1.9in}p{3in}p{.3in}p{1in}@{}}
  Faculty Advisor Signature: & \hrulefill & Date: & \hrulefill\\
\end{tabular}
\end{center}

\end{document}
